Algebraic Geometry\vspace{-1ex}

### 2020-02-14 Algebraic Geometry/Algebraic-Geometry.tex
Update

\begin{defn}
	A \textbf{test diagram} for a morphism $f:X\to Y$ is a diagram as in the figure below	
	where $i:R\hookrightarrow k=\kappa(R)$ is a vaulation ring.
	A \textbf{filling} for a test diagram is an arrow $\gamma:\Spec R\to X$ making this diagram commute.
\end{defn}
\begin{figure}[h]\label{fig:testdiagram}
	\centering
	\begin{tikzcd}
		\Spec k\ar[r]\ar[d,"i^\ast"] & X\ar[d,"f"]\\
		\Spec R\ar[r] & Y
	\end{tikzcd}
	\caption{A test diagram for $f$}
\end{figure}
\begin{thm}
	\begin{enumerate}
		\item A quasiseparated morphism $f:X\to Y$ is separated if and only if every test diagram has at most one filling.
		\item A quasicompact morphism $f:X\to Y$ is universally closed if and only if every test diagram admits at least one filling.
		\item A quasisemparated morphism of finite type $f:X\to Y$ is proper sif and only if every test digram admints precisely one filling.
	\end{enumerate}
\end{thm}
\begin{lem}
	The entire theorem above follows from (b).
\end{lem}
\begin{prf}
	To get (a) from (b), $f$ is quasiseparated iff $\Delta:X\to X\times_YX$ is quasicompact. Note that $f$ is separated iff $\Delta$ is 
	universally closed. Further, note that $\Delta$ is always an immersion. One can show that $\Delta$ is a closed immersion into an open subscheme (look in Hartshorne and use a cover by open affines).

@@

>>>>

\begin{defn}
	A \textbf{test diagram} for a morphism $f:X\to Y$ is a diagram as in the figure below	
	where $i:R\hookrightarrow k=\kappa(R)$ is a vaulation ring.
	A \textbf{filling} for a test diagram is an arrow $\gamma:\Spec R\to X$ making this diagram commute.
\end{defn}
\begin{figure}[h]\label{fig:testdiagram}
	\centering
	\begin{tikzcd}
		\Spec k\ar[r]\ar[d,"i^\ast"] & X\ar[d,"f"]\\
		\Spec R\ar[r] & Y
	\end{tikzcd}
	\caption{A test diagram for $f$}
\end{figure}
\begin{thm}\label{thm:fillings}
	\begin{enumerate}
		\item A quasiseparated morphism $f:X\to Y$ is separated if and only if every test diagram has at most one filling.
		\item A quasicompact morphism $f:X\to Y$ is universally closed if and only if every test diagram admits at least one filling.
		\item A quasisemparated morphism of finite type $f:X\to Y$ is proper sif and only if every test digram admints precisely one filling.
	\end{enumerate}
\end{thm}
\begin{lem}
	The entire theorem above follows from (b).
\end{lem}
\begin{prf}
	To get (a) from (b), $f$ is quasiseparated iff $\Delta:X\to X\times_YX$ is quasicompact. Note that $f$ is separated iff $\Delta$ is 
	universally closed. Further, note that $\Delta$ is always an immersion. One can show that $\Delta$ is a closed immersion into an open subscheme (look in Hartshorne and use a cover by open affines).

@@

\section{February 14th, 2020}
Max recommends probelm 4.10 from Hartshorne. It is the proof of Chow's lemma. It is not an easy proof, 
but it is a very important one.

\subsection{More generization and specialization}

\begin{lem}
	Given a quasicompact morphism $f:X\to Y$, $f(X)$ is closed in $Y$ if and only if it is \textit{closed under specialization}.
\end{lem}
\begin{prf}
	The conclistion is stable udner localiation on $U_i$, so we may assume $Y=\Spec A$. Then since $f$ is quasicompact, 
	$X=\cup_1^n\Spec B_i$ where $\Spec B_i=V_i$. But then 
	\[\Spec\prod B_i=\sqcup V_i\to X\to Y\]
	has the same image. Therefore we can assume that $X=\Spec B$ is affine.

	So we have a morphism $\Spec B\to \Spec A$, giving us a ring map $\varphi:A\to B$. So now if $I=\ker\varphi$,
	we get that the map $X\to Y$ factors through $\Spec A/I\hookrightarrow Y$, which is closed. So we can assume that $\varphi$ is injective.
	We want to show that $f(X)=Y$. \textit{Notice that we haven't checked that the assumption is closed under these reductions.}

	Now take any $p\in \Spec A$ and take a minimal prime $p_0\subseteq p$ (which exists by the standard Zorn argument).
	So now $p_0\rightsquigarrow p$. If $p_0\in f(X)$, then $p\in f(X),$ so $f(X)=Y$. Consider $A\hookrightarrow B$ and localize at $p_0$ (which preserves injectivity).
	and since $A_{p_0}$ has a single prime, you get a map with $p_0$ in the image. Thus you get $p$ and surjectivity.
\end{prf}

Now we are going to prove:
\begin{prf}[of thm.~\ref{thm:fillings}(b)]
	Assume that $f:X\to Y$ is universally closed. We want to show that fillings exist for any test diagram. Notice that fillings for test diagrams are equivalent 
	to finding sections (since we can assume $Y=\Spec R$):
	\begin{figure}[h]
		\centering
		\begin{tikzcd}
			\Spec k\ar[r,"\iota"]\ar[d] & X=X\times_{\Spec R}\Spec R\ar[d]\\
			\Spec R\ar[r,"\id"] & \Spec R\ar[u,bend right,dashed]
		\end{tikzcd}
	\end{figure}
	Let $x\in X$ be in the image of $\iota(\Spec k)$ and let $k$ be the resitude field of $x$. Let $z=\overline{\{x\}}\subseteq X$
	Now $(0)\subseteq f(z)\subset\Spec R$ is closed, so there exists $z\in Z$ such that $f(z)=\frakm_R$. I got lost at the end, but there were some diagrams that 
	boiled down to our ring being a valuation ring.

	Now assume that we have our fillings. Using the lemma, we can show that the image is cloed under specialization (warning: implicit base change being hidden here. If 
	we have $f:X\to Y$, $X_T\to T$).
\end{prf}
